
\bibliographystyle{unsrt}  
%\bibliography{references}  %%% Remove comment to use the external .bib file (using bibtex).
%%% and comment out the ``thebibliography'' section.


%%% Comment out this section when you \bibliography{references} is enabled.
\begin{thebibliography}{1}


\bibitem{alexnet}
Krizhevsky, Alex and Sutskever, Ilya and Hinton, Geoffrey E.
\newblock ImageNet Classification with Deep Convolutional Neural Networks
\newblock {\em Advances in Neural Information Processing Systems 25}, 2012

\bibitem{devlin2018bert}
Devlin, Jacob and Chang, Ming-Wei and Lee, Kenton and Toutanova, Kristina
\newblock BERT: Pre-training of Deep Bidirectional Transformers for Language Understanding
\newblock {\em arXiv preprint arXiv:1810.04805}, 2018

\bibitem{alvinn}
Dean A. Pomerleau.
\newblock ALVINN: An autonomous land vehicle in a neural network.
\newblock {\em Technical report, Carnegie Mellon University. URL:https://papers.nips.cc/paper/95-alvinn-an-autonomous-land-vehicle-in-a-neural-network.pdf}, 1989.

\bibitem{road}
Yann LeCun, Urs Muller, Jan Ben, Eric Cosatto, Beat Flepp.
\newblock Off-RoadObstacleAvoidancethroughEnd-to-EndLearning.
\newblock {\em URL:http://yann.lecun.com/exdb/publis/pdf/lecun-dave-05.pdf}, 2005.

\bibitem{deformable}
Mariolis I, Peleka G, Kargakos A, et al. 
\newblock Pose and category recognition of highly deformable objects using deep learning.
\newblock{\em Advanced Robotics (ICAR)}, 2015.

\bibitem{tactile}
Gao Y, Hendricks LA, Kuchenbecker KJ, et al.
\newblock Deep learning for tactile understanding from visual and haptic data.
\newblock {\em arXiv preprint arXiv:1511.06065}, 2015.
 
\bibitem{synergy}
Hwang J, Jung M, Madapana N, et al. 
\newblock Achieving "synergy" in cognitive behavior of humanoids via deep learning of dynamic visuo-motor-attentional coordination. 
\newblock{\em Humanoid Robots (Humanoids)}, 2015
 
\bibitem{manuver}
Jain A, Koppula HS, Soh S, et al. 
\newblock Brain4Cars: car that knows before you do via sensory-fusion deep learning architecture. 
\newblock {\em arXiv preprint arXiv:1601.00740}, 2016.

\bibitem{vanessa}
Vanessa Fernández Martinez
\newblock Conducción autónoma de un vehículo en simulador mediante aprendizaje extremo a extremo basado en visión
\newblock {\em Trabajo de Fin de Máster}, 2019.

\bibitem{transformers}
Vaswani, A., Shazeer, N., Parmar, N., Uszkoreit, J., Jones, L., Gomez, A. N., Kaiser, L., Polosukhin, I.
\newblock Attention is all you need.
\newblock {\em arXiv preprint arXiv:1706.03762}, 2017.
  
\bibitem{end2end}
Mariusz Bojarski, Davide Del Testa, Daniel Dworakowski, Bernhard Firner, Beat Flepp, Prasoon Goyal,Lawrence D Jackel, Mathew Monfort, Urs Muller, Jiakai Zhang.
\newblock End  to  end  learning  for  self-driving  cars.
\newblock {\em arXiv preprint arXiv:1604.07316}, 2016.

\bibitem{explaining-end2end}
Mariusz Bojarski, Philip Yeres, Anna Choromanska, Krzysztof Choromanski, Bernhard Firner, Lawrence Jackel, Urs Muller. 
\newblock Explaining How a Deep Neural Network Trained with End-to-End Learning Steers a Car.
\newblock {\em arXiv preprint arXiv:1704.07911}, 2017.

\bibitem{temporal-dependencies}
Hesham M. Eraqi, Mohamed N. Moustafa, Jens Honer.
\newblock End-to-End Deep Learning for Steering Autonomous Vehicles Considering Temporal Dependencies.
\newblock {\em arXiv preprint arXiv:1710.03804}, 2017.

\bibitem{imagenet}
Deng, J., Dong, W., Socher, R., Li, L.-J., Li, K., Fei-Fei, L.
\newblock ImageNet: A large-scale hierarchical image database
\newblock {\em CVPR}, 2009.

\bibitem{reactive-ground}
Keith Sullivan, Wallace Lawson.
\newblock Reactive Ground Vehicle Control via Deep Networks.
\newblock {\em URL:https://pdfs.semanticscholar.org/ec17/ec40bb48ec396c626506b6fe5386a614d1c7.pdf}, 2017.

\bibitem{deep-steering}
Lu Chi, Yadong Mu.
\newblock Deep Steering: Learning End-to-End Driving Model from Spatial and Temporal Visual Cues.
\newblock {\em arXiv preprint arXiv:1708.03798}, 2017.

\bibitem{interpretable}
Jinkyu Kim, John Canny.
\newblock Interpretable Learning for Self-Driving Cars by Visualizing Causal Attention.
\newblock {\em arXiv preprint arXiv:1703.10631}, 2017.

\bibitem{visual}
Mariusz Bojarski, Anna Choromanska, Krzysztof Choromanski, Bernhard Firner, Larry Jackel, Urs Muller, Karol Zieba.
\newblock VisualBackProp: efficient visualization of CNNs.
\newblock {\em arXiv preprint arXiv:1611.05418}, 2017.

\bibitem{survey-driving}
Gustav von Zitzewitz.
\newblock Survey of neural networks in autonomous driving.
\newblock {\em URL:https://www.researchgate.net/publication/324476862\_Survey\_of\_neural\_networks\_in\_autonomous\_driving}, 2017.

\bibitem{agile-autonomous}
Yunpeng Pan, Ching-An Cheng, Kamil Saigol, Keuntaek Lee, Xinyan Yan, Evangelos A. Theodorou, Byron Boots.
\newblock Agile Autonomous Driving using End-to-End Deep Imitation Learning.
\newblock {\em arXiv preprint arXiv:1709.07174}, 2018.

\bibitem{pixels}
Jonas Heylen, Seppe Iven, Bert De Brabandere, Jose Oramas M., Luc Van Gool, Tinne Tuytelaars.
\newblock From Pixels to Actions:Learning to Drive a Car with Deep Neural Networks.
\newblock In {\em IEEE Winter Conference on Applications of Computer Vision}, 2018.

\bibitem{event}
Ana I. Maqueda, Antonio Loquercio, Guillermo Gallego, Narciso García, Davide Scaramuzza.
\newblock Event-based Vision meets Deep Learning on Steering Prediction for Self-driving Cars.
\newblock In {\em  IEEE Conference on Computer Vision and Pattern Recognition}, 2018.

\bibitem{self-driving}
del Egio J., Bergasa L.M., Romera E., Gómez Huélamo C., Araluce J., Barea R.
\newblock Self-driving a Car in Simulation Through a CNN.
\newblock {\em In: Fuentetaja Pizán R., García Olaya Á., Sesmero Lorente M., Iglesias Martínez J., Ledezma Espino A. (eds) Advances in Physical Agents. WAF 2018. Advances in Intelligent Systems and Computing, vol 855. Springer, Cham}, 2019.

\bibitem{comma}
Eder Santana, George Hotz.
\newblock Learning a Driving Simulator.
\newblock {\em arXiv preprint arXiv:1608.01230}, 2016.

\bibitem{udacity-data}
Udacity.
\newblock Public driving dataset.
\newblock {\em URL:https://eu.udacity.com/course/self-driving-car-engineer-nanodegree--nd013}, 2017.

\bibitem{udacity-dataset}
Udacity's Datasets.
\newblock Public driving dataset.
\newblock {\em URL:https://github.com/udacity/self-driving-car/tree/master/datasets}, 2016.

\bibitem{nuscenes-dataset}
NuScenes's Datasets.
\newblock Public driving dataset.
\newblock {\em URL: https://www.nuscenes.org/}, 2019.

\bibitem{carla}
Alexey Dosovitskiy, German Ros, Felipe Codevilla, Antonio López, Vladlen Koltun.
\newblock CARLA: An Open Urban Driving Simulator.
\newblock {\em arXiv preprint arXiv:1711.03938}, 2017.

\bibitem{gazebo}
Gazebo.
\newblock Simulator.
\newblock {\em URL:http://gazebosim.org/}, 2018.

\bibitem{carla-org}
CARLA.
\newblock An Open Urban Driving Simulator.
\newblock {\em URL:http://carla.org/}, 2017.

\bibitem{udacity-sim}
 Udacity's Self-Driving Car Nanodegree.
\newblock Self-Driving Simulator.
\newblock {\em URL:https://github.com/udacity/self-driving-car-sim}, 2017.

\bibitem{kitti-sim}
Kitti's Self-Driving Car Nanodegree.
\newblock Karlsruhe Institute of Technology.
\newblock {\em URL:http://www.cvlibs.net/datasets/kitti/}, 2017.


\bibitem{deepdrive}
Deepdrive.
\newblock Self-Driving Simulator.
\newblock {\em URL:https://deepdrive.io/}, 2017.

\bibitem{jetsontk1}
NVIDIA Jetson TK1.
\newblock Embedded systems hardware
\newblock {\em URL:https://www.nvidia.com/object/jetson-tk1-embedded-dev-kit.html}, 2014.

\bibitem{jetsontx1}
NVIDIA Jetson TX1.
\newblock Embedded systems hardware
\newblock {\em URL:https://la.nvidia.com/object/jetson-tx1-dev-kit-la.html}, 2015.

\bibitem{jetsonnano}
NVIDIA Jetson Nano.
\newblock Embedded systems hardware
\newblock {\em URL:https://www.nvidia.com/es-es/autonomous-machines/embedded-systems/jetson-nano/}, 2019.

\bibitem{jetsonxavier}
NVIDIA Jetson Xavier.
\newblock Embedded systems hardware
\newblock {\em URL:https://www.nvidia.com/es-es/autonomous-machines/embedded-systems/jetson-agx-xavier/}, 2018.

\bibitem{tegrak1}
NVIDIA Tegra K1.
\newblock Embedded systems hardware
\newblock {\em URL:https://la.nvidia.com/object/tegra-k1-processor-la.html}, 2013.

\bibitem{sae}
Levels of Driving Automation.
\newblock Automate driving levels of driving automation are defined in new SAE International Standard J3016.
\newblock {\em URL:https://www.smmt.co.uk/wp-content/uploads/sites/2/automated\_driving.pdf}, 2017.

\bibitem{follow}
Follow line.
\newblock JdeRobot RoboticsAcademy.
\newblock {\em https://github.com/JdeRobot/RoboticsAcademy/tree/master/exercises/follow\_line}, 2019.

\bibitem{tpu}
Google TPU
\newblock Google.
\newblock {\em URL:https://cloud.google.com/tpu/docs/tpus}, 2019.

\bibitem{pfc}
Francisco Pérez Salgado
\newblock Caminatas basadas en ondas acopladas para el humanoide nao en Gazebo-5 y JdeRobot
\newblock {\em Proyecto final de carrera}, 2015.

\bibitem{geoffreyhinton}
Hinton, Geoffrey E., Simon Osindero, and Yee-Whye Teh.
\newblock A fast learning algorithm for deep beliefs
\newblock {\em Neural compuattion 18.7}, 2006.

\bibitem{deepface}
Taigman, Yaniv, et al.
\newblock Deepface: Closing the gap to human-level performance in face verification.
\newblock {\em Porceedings of the IEEE conference on computre vision and pattern recognition}, 2014.

\bibitem{resnet}
He, Kaiming et al.
\newblock Deep Residual Learning for Image Recognition.
\newblock In {\em IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, 2015.



\end{thebibliography}
